### 2016-04-14 ch01-intro/introduction.tex
Different figure names per chapter
Fix: biblatex 3.3 -> 3.4
Small changes here and there

\chapter{Introduction}
\def\thisDir{ch01-intro}
\myEpigraph{It's a dangerous business, Frodo, going out your door. You step onto the road, and if you don't keep your feet, there's no knowing where you might be swept off to.}{John Ronald Reuel Tolkien}{The Fellowship of the Ring}
  \section{System idenfication}

@@

% http://tex.stackexchange.com/questions/18664/underline-my-name-in-the-bibliography
\DeclareNameFormat{author}{%
\ifthenelse{\equal{#1}{Geerardyn}}%
    {\textbf{\ifblank{#3}{}{#3\space}#1}}%
    {\ifblank{#3}{}{#3\space}\ifblank{#5}{}{#5\space}#1}%
\ifthenelse{\value{listcount}<\value{liststop}}%
    {\addcomma\space}
    {}}

@@

The non-parametric estimation methods in \chapref{sec:nonparametric} are based on a yet-unpublished journal manuscript:
\begin{itemize}
  \item \TODO{Geerardyn2016LRM}
\end{itemize}
and the truncated \gls{LPM} presented in the same chapter is based on a journal published in \gls{IEEE} Transactions on Instrumentation \& Measurement:
\begin{itemize}
  \item \fullcite{Lumori2014TIM}.
\end{itemize}
Relatedly, a preliminary study of the \gls{LPM} in the context of lightly-damped \gls{MIMO} systems has been presented at the (non-refereed) Benelux Meeting on Systems and Control:
\begin{itemize}
    \item \fullcite{Verbeke2015Benelux}.
\end{itemize}

>>>>

\chapter{Introduction}
\def\thisDir{ch01-intro}
\tikzsetfigurename{ch01fig}
\myEpigraph{It's a dangerous business, Frodo, going out your door. You step onto the road, and if you don't keep your feet, there's no knowing where you might be swept off to.}{John Ronald Reuel Tolkien}{The Fellowship of the Ring}
  \section{System idenfication}

@@

% http://tex.stackexchange.com/questions/18664/underline-my-name-in-the-bibliography
% Plus see release notes of BIBLATEX 3.3/3.4
\DeclareNameFormat{author}{%
  \nameparts{#1}%
\ifthenelse{\equal{\namepartfamily}{Geerardyn}}%
    {\textbf{\ifblank{\namepartgiven}{}{\namepartgiven\space}\namepartfamily}}%
    {\ifblank{\namepartgiven}{}{\namepartgiven\space}\ifblank{\namepartprefix}{}{\namepartprefix\space}\namepartfamily}%
\ifthenelse{\value{listcount}<\value{liststop}}%
    {\addcomma\space}
    {}}

@@

The non-parametric estimation methods in \chapref{sec:nonparametric} are based on a yet-unpublished journal manuscript and the truncated \gls{LPM} presented in the same chapter is based on a journal published in \gls{IEEE} Transactions on Instrumentation \& Measurement:
\begin{itemize}
  \item \fullcite{Lumori2014TIM}.
\end{itemize}
Relatedly, a preliminary study of the \gls{LPM} in the context of lightly-damped \gls{MIMO} systems has been presented at the (non-refereed) Benelux Meeting on Systems and Control:
\begin{itemize}
    \item \fullcite{Verbeke2015Benelux}.
\end{itemize}
